Towards Transparency and Open Science

### 2023-02-13 manuscript.Rmd
increase width of abstract

  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}
fontsize: 11pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
geometry: "left=4cm, right=4cm, top=3.5cm, bottom=4.5cm, bindingoffset=5mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---

>>>>

  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}

  \let\oldabstract\abstract
  \let\oldendabstract\endabstract
  \makeatletter
  \renewenvironment{abstract}
  {\renewenvironment{quotation}%
                 {\list{}{\addtolength{\leftmargin}{-1cm} % change this value to add or remove length   to the the default
                          \listparindent 1.5em%
                          \itemindent    \listparindent%
                          \rightmargin   \leftmargin%
                          \parsep        \z@ \@plus\p@}%
                  \item\relax}%
                 {\endlist}%
  \oldabstract}
  {\oldendabstract}
  \makeatother
fontsize: 11pt
linestretch: 1.2
# https://practicaltypography.com/page-margins.html
# 3.81 to 5.08cm or 45-90 characters or 2-3 alphabets
geometry: "left=4cm, right=4cm, top=3.5cm, bottom=4.5cm, bindingoffset=5mm"
classoption: twoside
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
toc: false # it is manually placed
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---
